Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-26 autovi_paper.qmd
Trying to streamline this to make it a bit less convoluted.

VSS is defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution, and more details can be found in @li2024automated. This measure is based on the Kullback-Leibler (KL) divergence:

>>>>

VSS is an estimate of the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution; more details can be found in @li2024automated. The distance measure is based on the Kullback-Leibler (KL) divergence:
